### 2012-04-16 intention motor representation with corrado sinigaglia/conf lyon glasgow was spp submit rejected/intention and motor representation HANDOUT.tex
talk

\def \ititle {Intention and Motor Representation in Action Explanation}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
\date{}

@@

\begin{center}
{\Large
\textbf{Intention and Motor Representation in Action Explanation}
}

@@

\item My intention that I visit Paris on Friday is a propositional attitude.

>>>>

\def \ititle {Intention and Motor Representation in Purposive Action}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
\date{}

@@

\begin{center}
{\Large
\textbf{Intention and Motor Representation in Purposive Action}
}

@@

\item My intention that I visit Glasgow on Monday is a propositional attitude.
